\em \huge A CONSTRVCTIVE SOLVTION TO THE K\"ONIGS-PITTSBVRGH BRIDGE PROBLEM

### 2015-03-17 koenigs/koenigs-pittsburgh.tex
fix stuff in koenigs

\documentclass[twocolumn]{article}
\usepackage{fullpage}
%%\usepackage{amsmath}
%%\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{algpseudocode}
%%\usepackage{ulem}
%%\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subcaption}
%%\usepackage{phonetic}
%%\usepackage{synttree}

@@

\usepackage{mathspec}
%\usepackage{fouriernc}
%\usepackage[T1]{fontenc}
%\usepackage[veryoldstyle]{kpfonts}

@@

\usepackage{titlesec}
\titleformat{\section}
  {\normalfont\oldestyle\Large\bfseries}
  {\thesection}{1em}{}

@@

  \title{\em A CONSTRVCTIVE SOLVTION TO THE K\"ONIGS-PITTSBVRGH BRIDGE PROBLEM}
\author{Greg HANNEMAN\\
	Language Enthusiast and Errant Scribbler
	%\footnote{and Salaried Employee now too!}
	\\
        Carnegie Mellon Vniversity
	\and
	Benj. BLVM \\
	Light Cone Sedentarian \\
	Carnegie Mellon Vniversity}
\date{}
\pagestyle{empty}

@@

\begin{abstract}
	We walked across a bunch of bridges one day.
\end{abstract}

@@

\section*{\S 1 - Back-Ground}

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.48\textwidth]{koenigsburg.pdf}
	\caption{Kaliningrad, Russia (colloq.); better known in the formal literature as K\"onigsberg, Prussia}
	\label{fig:koenigs}
\end{figure}

@@

\section*{\S 2 - Formalization}

The formal statement of KBP inquires after the existence of an Eulerian path on a graph representing K\"onigsberg, with one node to represent each of the landmasses connected by various edges (bridges). In KPBP we simply change the graph to represent the topology of our home city (Figure \ref{fig:map}).\footnote{The astute observer will note that no edge among our formalism represents the $32^{\text{nd}}$ street bridge. During the progress of our research, this bridge did not exist due to construction, and hence is omitted. If added to the graph (call it KPBP'), it is known that a solution exists, but a constructive proof is left to future work.}

\begin{figure}[t]
\centering
	\includegraphics[width=0.35\textwidth]{1859pittsburgh.jpg}
	\caption{Informal Diagram of the Topology of Pittsburgh, Pennsylvania as Defined by its Bridges and Rivers.}
	\label{fig:map}
\end{figure}

@@

\section*{\S 3 - Proof}

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{ll}
	\begin{tabular}{|l|l|l|}
		\hline
		Node & Edge & Node \\
		\hline
		EE & HP & NS \\
		NS & 62 & EE \\
		EE & 40 & NS \\
		NS & 16 & EE \\
		EE & RaC & NS \\
		NS & AW & EE \\
		EE & RoC & NS \\
		NS & MKR & SS \\
		SS & WE & NS \\
		\hline
	\end{tabular}
	&
	\begin{tabular}{|l|l|l|}
		\hline
		Node & Edge & Node \\
		\hline
		NS & FtD & EE \\
		EE & FtP & SS \\
		SS & SF & EE \\
		EE & 10 & SS \\
		SS & Lib & EE \\
		EE & BH & SS \\
		SS & HMS & EE \\
		EE & GF & SS \\
		SS & HSG & EE \\
		\hline
	\end{tabular}
	\end{tabular}
	\caption{$|R|$ = 35 mi.}
	\label{tab:solution}
\end{table}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.48\textwidth]{solution.png}
	\caption{A cartographic rendering of the solution route $R$.}
	\label{fig:solution}
\end{figure}

@@

\begin{proc} \label{Proc-Walk}
Let $R$ be the given solution route for KPBP, $p$ be a position along it measured in miles from the start of $R$, and $\hat{r}_x$ be a unit vector in the direction of $R$ at position $x$.
\begin{algorithmic}
\While{$p < |R|$}
    \State $\vec{d} \gets \mathrm{StepSize} \cdot \hat{r}_p$
    \State $\mathrm{Walk}(p, \vec{d})$
    \State $p \gets p + ||\vec{d}||$
\EndWhile
\end{algorithmic}
\end{proc}

@@

Lemma \ref{Lemma-Walk} thus establishes a ``modus ponens'' result for traversal of the route $R$ from its beginning ($p = 0$) to its end ($p = |R|$).  This is, however, a purely theoretical result.  We now show the practicability of the solution in an operational scenario via a number of satisfiable conditions.

\begin{figure*}[b]
	\begin{tabular}{cc}
	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{initialization.png}
	\caption{Condition \ref{cond:init}, initialization.}
	\end{subfigure}
	&
	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{mckees.png}
	\caption{An example member of the set $B$.}
	\end{subfigure}
	\\

	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{mini-koenigs.png}
	\caption{$\exists b \in R~\text{s.t.}~b \not\in B$.}
	\end{subfigure}
	&
	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{finish.png}
	\caption{Condition \ref{cond:term}, successful termination.}
	\end{subfigure}

@@

Let $A$ be a set of attempting participants.  Then $a$ must be present at $p = 0 \forall~a \in A$.
\end{cond}

@@

Let $B$ be a set of qualifying bridges such that the following are true $\forall~b \in B$:  (1) $b$ satisfies the bridge criteria from Definition \ref{Def-KonigsPgh}; (2) $b$ has defined $0 \leq p_b \leq 35$ on $R$.  Let $b_i$ be the $i$th ordered element of $B$, and let $|B| = n$.  Then $C = \{c_1, ..., c_n\}$, and $c_i = (S_i, b_i)$ iff some $S_i \subseteq A$ crosses $b_i$.
\end{cond}

@@

Let the set of ending participants $E \subseteq A = \{ a \in A\,|\, a \in S_i\ \forall~i \}$.  Then the solution is successful iff $E \neq \emptyset$ and $e$ is present at $p = 35\ \forall~e \in E$.
\end{cond}

@@

\end{lemma}
\begin{proof}
	Set $A = \{$Alan, Ben, Dan, Greg, Keith$\}$. Note that $\Pr(x~\mathrm{awake~at~5~a.m.}) = \epsilon\ \forall~x \in A$. As long as $\epsilon > 0$, $\epsilon^5 > 0$ \cite{what-is-epsilon}.

Set $B = \{$Highland Park, 61st Street, 40th Street, 16th Street, 9th Street, 7th Street, 6th Street, McKees Rocks, West End, Fort Duquesne, Fort Pitt, Smithfield Street, Liberty, 10th Street, Birmingham, Hot Metal, Glenwood, Homestead Grays$\}$.
The bridge criteria of Definition \ref{Def-KonigsPgh} are satisfied $\forall~b \in B$. Therefore the set $C$ of crossings may be freely constructed following $R$ from Figure \ref{fig:solution}.

Set $E = \{$Alan, Ben, Greg$\}$.
The diagrams in Figure \ref{fig:photos} offer a visualization of these values.

Since $|E| = 3 > 0$, this proves Lemma \ref{lem:satisf} and thus the successful instantiation of Conditions 1--3.  Together with Lemma \ref{Lemma-Walk}, this proves that $R$ is a navigable Eulerian circuit of the city of Pittsburgh.  Therefore a solution to the K\"onigs-Pittsburgh Bridge Problem exists.
\end{proof}

\section*{\S 4 - Conclusion}

@@

\bibliographystyle{alpha}
\bibliography{sigbovik}

>>>>

\documentclass[twocolumn]{article}
\usepackage{fullpage}
%%\usepackage{amsmath}
%%\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{hyperref}
\usepackage{algpseudocode}
%%\usepackage{ulem}
%%\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subcaption}
%%\usepackage{phonetic}
%%\usepackage{synttree}

@@

%\usepackage{rotating}
\usepackage{mathspec}
%\usepackage{fouriernc}
%\usepackage[T1]{fontenc}
%\usepackage[veryoldstyle]{kpfonts}

@@

%\usepackage{titlesec}
%\titleformat{\section}
%  {\normalfont\oldestyle\Large\bfseries}
%  {\thesection}{1em}{}

@@

  \title{\em \huge A CONSTRVCTIVE SOLVTION TO THE K\"ONIGS-PITTSBVRGH BRIDGE PROBLEM}
\author{Greg HANNEMAN\\
	Language Enthusiast and Errant Scribbler
	%\footnote{and Salaried Employee now too!}
	\\
        Carnegie Mellon Vniversity
	\and
	Benj. BLVM \\
	Light Cone Sedentarian \\
	Carnegie Mellon Vniversity}
\date{}
\pagestyle{empty}

@@

\section*{ABSTRACT.}
	We walked across a bunch of bridges one day.

@@

\section*{\S 1..... BACKGROVND.}

@@

\begin{figure}[h]
\centering
	\includegraphics[width=0.48\textwidth]{koenigsburg.pdf}
	\caption{Kaliningrad, Russia (colloq.); better Known in the Formal Literature as K\"onigsberg, Prussia}
	\label{fig:koenigs}
\end{figure}

@@

\section*{\S 2..... FORMALIZATION.}

The formal statement of KBP inquires after the existence of an Eulerian path on a graph representing K\"onigsberg, with one node to represent each of the landmasses connected by various edges (bridges). In KPBP we simply change the graph to represent the topology of our home city (Figure \ref{fig:map}).\footnote{The astute observer will note that no edge among our formalism represents the $32^{\text{nd}}$ street bridge. During the progress of our research, this bridge did not exist due to construction, and hence is omitted. If added to the graph (call it KPBP'), it is known that a non-cyclic solution exists, but a constructive proof is left to future work.}

\begin{figure}[t]
\centering
	\includegraphics[width=0.35\textwidth]{1859pittsburgh.jpg}
	\caption{informal Diagram of the Topology of Pittsburgh, Pennsylvania as defined by its Bridges and Rivers.}
	\label{fig:map}
\end{figure}

@@

\section*{\S 3..... PROOF.}

@@

\begin{table}[b]
	\centering
	\small
	\begin{tabular}{ll}
	\begin{tabular}{|l|l|l|}
		\hline
		Node & Edge & Node \\
		\hline
		EE & HP & NS \\
		NS & 62 & EE \\
		EE & 40 & NS \\
		NS & 16 & EE \\
		EE & RaC & NS \\
		NS & AW & EE \\
		EE & RoC & NS \\
		NS & MKR & SS \\
		SS & WE & NS \\
		\hline
	\end{tabular}
	&
	\begin{tabular}{|l|l|l|}
		\hline
		Node & Edge & Node \\
		\hline
		NS & FtD & EE \\
		EE & FtP & SS \\
		SS & SF & EE \\
		EE & 10 & SS \\
		SS & Lib & EE \\
		EE & BH & SS \\
		SS & HMS & EE \\
		EE & GF & SS \\
		SS & HSG & EE \\
		\hline
	\end{tabular}
	\end{tabular}
	\caption{|R| = 35 mi.}
	\label{tab:solution}
\end{table}

@@

\begin{proc} \label{Proc-Walk}
Let $R$ be the given solution route for KPBP, $p$ be a position along it measured in miles from the start of $R$, and $\hat{r}_x$ be a unit vector in the direction of $R$ at position $x$.
\end{proc}

%%%%%%%%%%%%%
%\newpage
%\begin{turn}{1}
%\begin{minipage}{\textwidth}
%\begin{multicols}{2}

\begin{algorithmic}
\While{$p < $|R|}
    \State $\vec{d} \gets \mathrm{StepSize} \cdot \hat{r}_p$
    \State Walk($p, \vec{d}$)
    \State p $\gets$ p + ||$\vec{d}$||
\EndWhile
\end{algorithmic}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.48\textwidth]{solution.png}
	\caption{a cartographic Rendering of the Solution Route $R$.}
	\label{fig:solution}
\end{figure}

Lemma \ref{Lemma-Walk} thus establishes a ``modus ponens'' result for traversal of the route $R$ from its beginning (p = 0) to its end (p = |R|).  This is, however, a purely theoretical result.  We now show the practicability of the solution in an operational scenario via a number of satisfiable conditions.

@@

Let $A$ be a set of attempting participants.  Then $a$ must be present at p = 0 \forall{}a $\in$ A.
\end{cond}

@@

Let $B$ be a set of qualifying bridges such that the following are true \forall{}b $\in$ B:  (1) $b$ satisfies the bridge criteria from Definition \ref{Def-KonigsPgh}; (2) $b$ has defined 0 $\leq$ $p_b$ $\leq$ 35 on $R$.  Let $b_i$ be the $i$th ordered element of $B$, and let |B| = n.  Then C = \{$c_1, ..., c_n$\}, and $c_i$ = ($S_i, b_i$) iff some $S_i \subseteq A$ crosses $b_i$.
\end{cond}

@@

Let the set of ending participants $E \subseteq A$ = \{$a \in A\,|\, a \in S_i\ \forall{}i$\}.  Then the solution is successful iff $E \neq \emptyset$ and $e$ is present at p = 35 \forall{}e $\in$ E.
\end{cond}

@@

\end{lemma}
\begin{proof}
	Set A = \{Alan, Ben, Dan, Greg, Keith\}. Note that Pr(x  awake at 5 a.m.) = $\epsilon$ \forall{}x $\in$ A. As long as $\epsilon$ > 0, $\epsilon^5$ > 0. \cite{what-is-epsilon}

Set B = \{Highland Park, 61st Street, 40th Street, 16th Street, 9th Street, 7th Street, 6th Street, McKees Rocks, West End, Fort Duquesne, Fort Pitt, Smithfield Street, Liberty, 10th Street, Birmingham, Hot Metal, Glenwood, Homestead Grays\}.
The bridge criteria of Definition \ref{Def-KonigsPgh} are satisfied $\forall{}b \in B$. Therefore the set $C$ of crossings may be freely constructed following $R$ from Figure \ref{fig:solution}.

Finally, set E = \{Alan, Ben, Greg\}.
The diagrams in Figure \ref{fig:photos} offer a visualization of these values for A, B, and E.

Since |E| = 3 > 0, this proves Lemma \ref{lem:satisf} and thus the successful instantiation of Conditions 1--3.  Together with Lemma \ref{Lemma-Walk}, this proves that $R$ is a navigable Eulerian circuit of the city of Pittsburgh.  Therefore a solution to the K\"onigs-Pittsburgh Bridge Problem exists.
\end{proof}

\section*{\S 4..... CONCLVSION.}

@@

\renewcommand\refname{REFERENCES.}
\bibliographystyle{alpha}
\bibliography{sigbovik}

%%%%%%%%%%%%%
%\end{multicols}
%\end{minipage}
%\end{turn}
%\newpage

\begin{figure*}[b]
	\begin{tabular}{cc}
	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{initialization.png}
	\caption{Condition \ref{cond:init}, Initialization.}
	\end{subfigure}
	&
	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{mckees.png}
	\caption{an example Member of the set $B$.}
	\end{subfigure}
	\\

	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{mini-koenigs.png}
	\caption{\exists b $\in$ R s.t. b $\not\in$ B.}
	\end{subfigure}
	&
	\begin{subfigure}[b]{0.45\textwidth}
	\centering
	\includegraphics[width=\textwidth]{finish.png}
	\caption{Condition \ref{cond:term}, successful Termination.}
	\end{subfigure}
